The reference model approach in feature selection problems \vspace{.1in}

### 2019-07-12 paper/ref_approach.tex
minor edits + BDA3 bibref

The main assumption under any reference model approach is that we
operate in a $\mathcal{M}$-\textit{complete} framework
\citep{book:bernardo_smith,vehtari2012survey}, that is we have constructed a
model which reflects in the best way our beliefs about the future
data. In practice, this would often be the full-encompassing model
(including as submodels all models we consider having non-zero prior
probability) which has passed model checking and criticism \citep[see,
e.g.][]{BDA3}.

@@

When using a reference model, we first model $f$ using all the covariates $\{X_{j}\}_{j=1}^{p}$ taking into account that we observe noisy $Y$. If our model is good, we are able to describe $f$ better than the noisy $Y$, which imporves the accuracy in the estimation of the relevance of the covariates.  Figure \ref{fig:correlation} shows the scatter plot of the absolute value of the sample correlation of each feature with the point prediction by a reference model, in this case see model \eqref{eq:ref_mod}, against the absolute value of the sample correlation of each feature with the noisy observations $\{y\}_{i=1}^{n}$. Looking at the marginal distributions, we can see that using a reference model to filter out noise in the data the two groups of features (relevant and non-relevant) can be better distinguished than when the correlation is computed using directly using only the observed noisy data.

>>>>

The main assumption under any reference model approach is that we
operate in a $\mathcal{M}$-\textit{complete} framework
\citep{book:bernardo_smith,vehtari2012survey}, that is we have constructed a
model which reflects in the best way our beliefs about the future
data. In practice, this would often be the full-encompassing model
(including as submodels all models we consider having non-zero prior
probability) which has passed model checking and criticism \citep[see,
e.g.][]{gelman2013bayesian}.

@@

When using a reference model, we first model $f$ using all the covariates $\{X_{j}\}_{j=1}^{p}$ taking into account that we observe noisy $Y$. If our model is good, we are able to describe $f$ better than the noisy $Y$, which imporves the accuracy in the estimation of the relevance of the covariates.  Figure \ref{fig:correlation} shows the scatter plot of the absolute value of the sample correlation of each feature with the point prediction by a reference model, in this case see model \eqref{eq:ref_mod}, against the absolute value of the sample correlation of each feature with the noisy observations $\{y\}_{i=1}^{n}$. Looking at the marginal distributions, we can see that using a reference model to filter out noise in the data the two groups of features (relevant and non-relevant) can be better distinguished than when the correlation is computed using directly the observed noisy data.
